---
title: "Project Template"
author: "Brady Chiu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    css: ./formatting.css
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
---

# TL;DR

```{r message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
knitr::read_chunk("../code/main.R")
knitr::opts_chunk$set(fig.height=5, fig.width=8)
```
```{r setup, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r functions, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r parameters, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_4, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_5, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```

# Exploring Patterns



# Data Quality Check

```{r data_sanity_check_1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

We see three odd things about our data, and will do what we can to fix them:

1.  Month of 2014-04 has an unusual spike in trip volume
2.  Month of 2014-09 is the only month where entries out pace exists
3.  Exits outpace entries every month

## Part 1

Month of 2014-04 has an unusual spike in trip volume.

```{r data_sanity_check_2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

Investigating our raw data shows dup rows for this month, so we'll go ahead and dedup rows for that month.

```{r data_sanity_check_3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Part 2

We see month of 2014-09 is the only month where entries out pace exists.

We'll correct for this by editing exits for that month to be the "# of entries in 2014-09" + "average difference between exits and entries".

```{r data_sanity_check_4, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Part 3

Lastly, exits outpace entries every month. In reality, a vehicle that exits had to have entered at some point, and vice versa. 

For our analysis, we only need one number per month, so we'll use the maximum of each months entry or exit.

```{r data_sanity_check_5, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Data Setup

To setup our data, we'll take the last 6 weeks and set them aside for validation. We'll use the remaining data to train our models.

```{r data_setup, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

# Code
```{r setup, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r functions, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r parameters, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_1, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_2, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_3, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_4, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_5, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_setup, message=FALSE, warning=FALSE, eval=FALSE}
```