---
title: "Project Template"
author: "Brady Chiu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    css: ./formatting.css
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
---

# TL;DR

* __Objective:__ Forecast LAX ground vehicle traffic volume for the year of 2017
* __Apporach:__ We assessed 3 forecasting models: STL Decomposition, Holt-Winters Exponential Smoothing, and Arima  
* __Finding:__ STL Decomposition forecasting was most accurate, predicting ~40MM vehicles will pass through LAX in 2017

```{r message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
knitr::read_chunk("../code/main.R")
knitr::opts_chunk$set(fig.height=5, fig.width=8)
```
```{r setup, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r functions, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r parameters, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_4, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```
```{r data_sanity_check_5, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, include=FALSE}
```

# Setup

## Validation Data

To setup the data for our analysis, we'll take the last `r validation_periods` months and set them aside for validation. We'll use the remaining data to train our models.

```{r data_setup, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Exploring Patterns

As expected with travel patterns, we see relatively strong 12 month seasonality:

* February is consistently the lowest month  
* July / August / December are consistently the highest months  
* Dips consistently occur during September / October / November periods  

```{r exploring_patterns, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Stationary

Before proceeding, we'll need to make our data stationary over time, so we'll start with an integrated of order 1 and see if it becomes stationary.

```{r diff1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### ACF

Our Autocorrelation Function (ACF) shows significance at lag 12 and almost significance at lag 24. This makes intuitive sense as travel data is seasonal on an annual level.

```{r acf, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Ljung-Box

Our Ljung-Box test shows statistical significance, validating I(1) is stationary.

```{r ljung-box, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### ADF

Our Augmented Dickey-Fuller (ADF) test shows statistical significance at a p-value < 0.05, validating I(1) is stationary.

```{r adf, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### KPSS

Our Kwiatkowski-Phillips-Schmidt-Shin (KPSS) test shows no statistical significance at a p-value < 0.05, validating I(1) is stationary.

```{r kpss, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

# Model Selection

We'll run forecasting using our three models:

* STL Decomposition  
* Holt-Winters Exponential Smoothing  
* Arima  

## STL Decomposition

### Analysis

```{r stl_analysis, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Validation

```{r stl_validation, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Holt-Winters Exponential Smoothing

### Analysis

```{r hw_analysis, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Validation

```{r hw_validation, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Arima

### Analysis

```{r arima_analysis, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Validation

```{r arima_validation, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Model Comparison

We compared our models using the following error metrics:  
* Mean Absolute Error  
* Mean Absolute Percentage Error  
* Mean Squared Error    
* Mean Percentage Error  

```{r model_comparison, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

Our STL Decomposition model performed the best

# Forecasting

We'll use our STL Decomposition to project LAX ground vehicles 2 years out

```{r final_forecast, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

# Appendix

## Data Quality Check

```{r data_sanity_check_1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

We see three odd things about our data, and will do what we can to fix them:

1.  Month of 2014-04 has an unusual spike in trip volume
2.  Month of 2014-09 is the only month where entries out pace exists
3.  Exits outpace entries every month

### Part 1

Month of 2014-04 has an unusual spike in trip volume.

```{r data_sanity_check_2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

Investigating our raw data shows dup rows for this month, so we'll go ahead and dedup rows for that month.

```{r data_sanity_check_3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Part 2

We see month of 2014-09 is the only month where entries out pace exists.

We'll correct for this by editing exits for that month to be the "# of entries in 2014-09" + "average difference between exits and entries".

```{r data_sanity_check_4, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

### Part 3

Lastly, exits outpace entries every month. In reality, a vehicle that exits had to have entered at some point, and vice versa. 

For our analysis, we only need one number per month, so we'll use the maximum of each months entry or exit.

```{r data_sanity_check_5, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
```

## Code
```{r setup, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r functions, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r parameters, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_1, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_2, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_3, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_4, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_sanity_check_5, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r data_setup, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r exploring_patters, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r diff1, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r acf, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r ljung-box, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r adf, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r kpss, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r create_ts, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r stl_analysis, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r stl_validation, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r hw_analysis, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r hw_validation, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r arima_analysis, message=FALSE, warning=FALSE, eval=FALSE}
```
```{r arima_validation, message=FALSE, warning=FALSE, eval=FALSE}
```